Quality Definitions of Qualities

### 2019-12-14 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated installaility

\begin{defn}
  A measure of the ease of installation \citep{smith2015comparing}.\wss{Where
    does this definition come from? Please add a citation.  Is it from
    \citet{McCallEtAl1977}? I thought so originally, but after looking into it,
    I don't think so anymore.}  \oo{@smith you added the definition in here but
    I guess it's from here} \wss{@olu, I was hoping you would verify the source
    of the definition.  Can you please find a pdf of the McCall reference and
    add it to our pub repo.  We should cite the primary source, but we can't
    assume what it says.  The source is definitely NOT
    \citep{smith2015comparing}.  By the way, you should use the BibTeX entries
    from References.bib in the pub repo when they are available.  This will save
    you time and make the citations more accurate. }  \wss{Olu, once we have the
    McCall reference, please verify all of the definitions where it is used, and
    remove the reference to the Van Vliet textbook.}
\end{defn}

\begin{defn}
  The capability of a software product to be installed in a specified
  environment \citep{ISO9126}. (As summarized in
  \citep{berander2005software}.)  \wss{remove the quotation marks - we are
    assuming all definitions are directly quoted from the source. Please remove
    quotes for all of the definitions that you ``own.''}  \oo{Done} \wss{I've
    verified that this definition is correct.  We do not have to cite the
    textbook anymore, since we have the original source.  Olu, please remove the
    \citep{berander2005software} in all instances where we have verified with
    the original source.}
\end{defn}

@@

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the cost or
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.  \wss{This definition does not
  allow for measuring the machine time.  Do we want to distinguish between the
  human effort required and the total time of installation?  I think the human
  effort is the important metric here.}

@@

\wss{The rationale is missing.  Please add.} \oo{Done} The definition captures
the cost or effort - human or machine, and considers not just the initial
installation but uninstallation and re-installation which are all related to
installation activities.  \oo{Done installability}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\subsection{\notdone{Verifiability/Testability} \oo{owner}}

@@

\begin{defn}
  Attributes of software that relate to the effort needed for validating the
  modified software \citep{iso2001iec}.
\end{defn}

\begin{defn}
  Effort required to test a program to ensure that it performs its intended
  function \citep{McCallEtAl1977}. (As summarized in
  \citet{pressman2005software})
\end{defn}

\begin{defn}
	The effort required to test a program to ensure that it performs its
	intended function \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.) \oo{similar to \citep{pressman2005software}, this}
\end{defn}

\begin{defn}
  Testability is the degree to which a requirement is stated in terms that
  permits establishment of test criteria and performance of tests to determine
  whether those criteria have been met \citep{IEEEStdGlossarySET1990}
\end{defn}

\begin{defn}
  Code possesses the characteristic testability to the extent that it
  facilitates the establishment of verification criteria and supports evaluation
  of its performance \citep{boehm1976quantitative}.
\end{defn}

\begin{defn} \label{Defn_Verifiability1} 
  Testability is the degree to which a system or component facilitates the
  establishment of test criteria and the performance of tests to determine
  whether those criteria have been met \citep{ISO/IEC/IEEE24765}.
\end{defn}

\begin{defn} \label{Defn_Verifiability2} 
  Testability is the effort required to test a software
  \citep{ISO/IEC/IEEE24765}.
\end{defn}

\begin{defn}
Testability is the capability of the software product to enable modified
software to be validated \cite{ISO9126}.
\end{defn}

@@

Combined definitions~\ref{Defn_Verifiability1} and~\ref{Defn_Verifiability2}
rephrased: Testability or verifiability is the degree to which a system or
component facilitates the establishment of test criteria and the performance of
tests to determine whether those criteria have been met and the effort required
to test.

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
  \citep{WikipediaVnV} \wss{This reference is not appearing in the Reference
    list.  We also don't really want a Wikipedia citation in a scholarly paper.
    Can you please find the source where this definition originally came from?}
\end{defn}

@@

Definition~\ref{} \oo{need to discuss this quality, we might just define
  validatability from validation definitions above? Resources are limited for
  'validatability'}.

@@

\begin{defn}
 The capability of the software to maintain the level of performance of the
 system when used under specified conditions \cite{ISO9126}.
\end{defn}

\begin{defn} \label{reliabilitySelected1} Probability of failure-free operation
  of a computer program in a specified environment for a specified time
  \citep{musa1987software}. (As stated in \citet{pressman2005software}.)
\end{defn}

@@

\begin{defn}
  The extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.) \wss{When we have a copy of the McCall reference we can
    verify this and simply cite the primary source.}
\end{defn}

@@

There are two ISO standards covering this, namely ISO/TR 16982:202 and ISO 9241.

>>>>

\begin{defn}
  The capability of the software product to be installed in a specified
  environment \citep{ISO9126}.\citep{ISO9126}
\end{defn}

@@

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.  \wss{I think the human
  effort is the important metric here.}

@@

 The definition captures a vital metric of measure for this quality - effort, and considers not just the installation but uninstallation and re-installation which are all related toinstallation activities.  \oo{Done installability}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with Mccall}
\end{defn}

@@

\subsection{\notdone{Verifiability} \oo{owner}}

@@

\begin{defn} \label{Defn_Verifiability1}
  Attributes of software that relate to the effort needed for validating the
  modified software \citep{iso2001iec}.
\end{defn}

\begin{defn}
  Effort required to test a program to ensure that it performs its intended
  function \citep{McCallEtAl1977}. (As summarized in
  \citet{pressman2005software})\oo{McCall defined this as testability not verifiability}
\end{defn}

\begin{defn}
	The effort required to test a program to ensure that it performs its
	intended function \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.) \oo{similar to \citep{pressman2005software}, this}
\end{defn} \oo{McCall defined this as testability not verifiability}

@@

Combined definitions~\ref{Defn_Verifiability1}
rephrased: Testability or verifiability is the degree to which a system or
component facilitates the establishment of test criteria and the performance of
tests to determine whether those criteria have been met and the effort required
to test.

@@

\begin{defn}
  Software validation checks that the software product satisfies or fits the
  intended use (high-level checking), i.e., the software meets the user
  requirements, not as specification artifacts or as needs of those who will
  operate the software only; but, as the needs of all the stakeholders (such as
  users, operators, administrators, managers, investors, etc.)
   \wss{This reference is not appearing in the Reference
    list.  We also don't really want a Wikipedia citation in a scholarly paper.
    Can you please find the source where this definition originally came from?}
\end{defn}

@@

Definition~ \oo{need to discuss this quality, we might just define
  validatability from validation definitions above? Resources are limited for
  'validatability'}.

@@

\begin{defn}
 The capability of the software product to maintain a specified level of performance when used under specified conditions \cite{ISO9126}.
\end{defn}

\begin{defn} \label{reliabilitySelected1} 
	It is the probability of failure-free operation of a computer program in a specified environment for a specified time
    \citep{musa1987software}.
\end{defn}

@@

\begin{defn}
  The extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. \oo{Check definition with pdf}
\end{defn}

@@

There are two ISO standards covering this, namely ISO/TR 16982:202 and ISO9241.
